---
title: "05-Flowchart"
author: "Marie Plessz"
date: "20/11/2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)  # for %>% pipes
library(DiagrammeR)
library(DiagrammeRsvg)  # for conversion to svg
library(rsvg)  # for saving svg
```

85,069 individuals were excluded because they joined the sample after 2016; 26,603 people were excluded because they were older than 60 at follow-up; 3,010 individuals were excluded because of missing information on employment; 19,880 individuals were excluded because they had a status other than “employed” at inclusion; 28,587 individuals were excluded because they either had no follow-up information or no information on employment at follow-up; 10,157 were excluded because of missing values on outcome variables when all constructed outcome variables were merged onto the same file to ensure a uniform sample file at inclusion.


```{r diagram}

flowchart <- grViz("digraph flowchart {
	node [fontname = Helvetica, shape = rectangle, fontsize = 9]
	in0 [label = 'Cohorte Constances  \\n N=199 711 '][group=g1]
	in1 [label = 'Inclusion 2012-2016 \\n n=114 642'][group=g1]
  in2 [label = 'Âge (inclusion) 18-60 ans \\n n=88 039'][group=g1]
  in3 [label = 'En emploi (inclusion) \\n n=68 159 '][group=g1]
  in4 [label = 'Suivi 2017 reçu \\n n=44 794'][group=g1]
  in5 [label = 'En emploi ou chômage (2017) \\n n=39 572 (dont 1049 au chômage)'][group=g1][fontsize = 8]
  in6 [label = 'Cas complets n=30 561 \\n (dont 718 au chômage 2017)'][group=g1]

  ex1 [label = 'Inclus après 2016 \\n n=85 069 '][style=rounded]
  ex2 [label = 'Âge (inclusion) >60  \\n n=26 603'][style=rounded]
  ex3 [label = 'Statut manquant (inclusion) \\n n=3010 '][style=rounded]
  ex3b [label = 'Autre statut \\n n=16 870'][style=rounded]
  ex4 [label = 'Suivi 2017 manquant \\n n=23 365'][style=rounded]
  ex5 [label = 'Statut manquant (2017) \\n n=1780'][style=rounded]
  ex5b [label = 'Autre statut (2017) \\n n=3442'][style=rounded]
  ex6 [label = 'Cas incomplets \\n n=9011'][style=rounded]
  
  
  in0 -> in1 -> in2 -> in3 -> in4 -> in5 -> in6
  in0 -> ex1
  in1 -> ex2
  in2 -> ex3
  in2 -> ex3b
  in3 -> ex4
  in4 -> ex5 
  in4 -> ex5b
  in5 -> ex6
}") 

flowchart

```
Export décevant. j'ai sauvé "manuellement".

```{r export}
flowchart %>%
     export_svg()    %>%
     charToRaw %>% 
#		rsvg::rsvg_png("Resultats/05_flowchart.png")
    rsvg_pdf("Resultats/05_flowchart.pdf")
```

